A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-08 docs/methods/erosion_methods.tex
worked on conclusion .... suddenly kids need to discuss future odd squad seasons they plan to write

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{s:conclusions}}
We have developed a numerical framework for simulating two-dimensional
Stokesian erosion in a porous media.  By using a BIE formulation of the
fluid equations and a {\thL}, we achieve spectral accuracy in space and
second-order accuracy in time.  In addition, the non-negligible
interactions between different bodies are accurately resolved.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{s:conclusions}}
We have developed a numerical framework for simulating two-dimensional
Stokesian erosion in a porous media.  By using a BIE formulation of the
fluid equations and a {\thL} change of variables, we achieve spectral
accuracy in space and second-order accuracy in time.  In addition, the
non-negligible interactions between different bodies are accurately
resolved.  Using slender body theory and flow past a wedge, the method
is verified against analytical results for the area, opening angle, and
total drag of a single eroding body.  Then, for multi-body erosion, a
more realistic pressure drop boundary condition, and we compute the area
fraction, flow rate, and total drag in the channel.
